\Large \bf Dark Decoys: Conjuring Proxies from Unused Address Space

### 2019-02-15 paper/paper.tex
updated WF text

\paragraph{Website Fingerprinting}
Dark Decoy applications that mimic websites (e.g. mask sites) may be vulnerable
to website fingerprinting, where the censor observes that clients accessing
suspected dark decoy IPs are receiving payloads or packet timings that differ
from legitimate connections to the mask site. This attack is difficult for
censors to carry out because it has high uncertainty: even a small false
positive rate means blocking mostly legitimate connections (due to the base rate
of normal traffic), and false negatives could allow clients to retry until they
gain access. More importantly, unlike previous Refraction Networking protocols,
Dark Decoy applications are not limited to mimicking websites, and can support
any (or even a combination of) protocols.

%\paragraph{Probing Dark Decoys}
%-Active probing TLS connection
%    -Block access unless from registering source IP
%        -cite GFW taking over client IPs for active probing of old obfs
%    -Verify knowledge of seed (but how to respond when verification fails?)

>>>>

\paragraph{Website Fingerprinting}

Website Fingerprinting~\cite{kNN,kFP,DLFP} (WF) uses the patterns of encrypted traffic to identify which website a client is connected to. WF uses a classifier to label the traffic as belonging to one of several known websites, or (in some variants), an unknown or background class. Though WF is commonly studied in the context of anonymous web browsing, a censor could also use WF to detect refraction networking by distinguishing known traffic patterns of legitimate uses of a decoy site from the traffic generated by refraction networking (unknown class). Alternatively, the censor could monitor all traffic for patterns consistent with a set of blocked websites.

Dark Decoy applications that mimic specific websites (e.g., mask sites) are likewise susceptible to WF. To date, however, censors have not been observed using WF and similar techniques, possibly due to the significant uncertainty resulting from even the best algorithms: even a small false
positive rate means blocking mostly legitimate connections (due to the base rate
of normal traffic), and false negatives could allow clients to retry until they
gain access.

More importantly, Dark Decoy applications offer great flexibility in deploying traffic analysis defenses; for example, traffic shaping strategies such as implemented in Slitheen~\cite{slitheen16} could be easily employed in Dark Decoys. Furthermore,
Dark Decoy applications are not limited to mimicking websites, and can support
any (or even a combination of) protocols. Finally, if encrypted SNI can be used (\cref{esni}), the censor would not be able to build up a traffic profile of a legitimate site since its identity would be encrypted.
